Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Liberal use of mathit

@@

The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
of his schedule in the array of constrained integer variables $timeSlot[0]$
to $timeSlot[{t-1}]$ (equation \ref{eq3} below), and a state view in the array of
constraint integer variables $state[0]$ to $state[{f-1}]$ (equation \ref{eq4}
below), i.e. $state[i]$ is the state of this skipper in flight $i$ and
corresponds to timeslots $timeSlot[{i*m}]$ to $timeSlot[{m(i+1)-1}]$.

\begin{flalign}
& f = \lceil n(n-1)/m  \rceil \label{eq1} \\
& t = n(n-1)/2 \label{eq2} \\
& \forall_{\tau \in [0..t-1]} ~ timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
& \forall_{i \in [0..f-1]} ~ state[{i}] \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
& \forall_{i \in [0..f]} ~ state[{i}] = FIRST \iff timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
& \forall_{i \in [0..f]} ~ state[{i}] = MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ timeSlot[{j}] \geq 0  \label{eq6} \\
& \forall_{i \in [0..f]} ~ state[{i}] = LAST \iff timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
& \forall_{i \in [0..f]} ~ state[{i}] = BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ timeSlot[j] = -1  \label{eq8} \\
& \forall_{i \in [0..f]} ~ state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ timeSlot[j] = -2  \label{eq9} \\
& globalCardinality(timeSlot,\{0,..,n-1\} \setminus \{\sigma\},\{1..1\},\{1 .. 1\})
\end{flalign}

In (\ref{eq3}) the array $timeSlot$ is defined and in (\ref{eq4}) $state$ is defined. If variable $timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a match with skipper $k$ at time $i$. Variable $state[{i}]$ gives the state of this skipper in flight $i$. The skipper can be in a match in the first time slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{... actually, not first and not last.} (\ref{eq6}) or in the last time slot of the flight (\ref{eq7}). If all time slots in a flight are equal to -1 then the skipper is in a bye (\ref{eq8}) and if all time slots in a flight are equal to -2 then the skipper has finished all his matches (\ref{eq9}).

A global cardinality constraint \cite{globCard} is then imposed on the array $timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all other skippers (i.e. $\{0 .. n-1 \} \setminus \{\sigma\}$) once (i.e. $\{1 .. 1\}$) and once only (i.e. $\{1 .. 1\}$). The $state$ variables are then used to impose match race criteria 4 (if last in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then flight $i$ is not first). In addition, we have the rule that if a skipper has finished his matches in flight $i$ (i.e. END) then he has finished his matches in flight $i+1$ (and so on). These criteria are imposed on the $state$ variables via a deterministic finite automata (dfa) constraint \cite{Pesant04}.

The constraints above are shown pictorially in Figure \ref{skipper5}, and corresponds to skipper 5 in the Table \ref{tab1} schedule. The $state$ array is presented as coloured boxes, and below that the $timeSlot$ array. The arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The $state$ array is coloured with green representing LAST, yellow for MID, blue for FIRST, red for LAST and (not shown) pink for BYE. The schedule of Table \ref{tab1} is reproduced with the matches for skipper 5 emboldened. To the right of the schedule is schema for the dfa. Coloured arc represent a transition from one state to another. The dfa is encoded as a set of transition objects $\langle q_{i},\iota,q_{j} \rangle$ where a transition is made from state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we specify the accepting states, being all states except the start state (white) and bye state (pink).

A boat change occurs when a skipper has been in a BYE state in flight $i$ and then is in a match in the next flight $i+1$. This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $totalChange$ (\ref{eq12}).

\begin{flalign}
    & \forall_{i \in [0..f-2]} ~ change[{i}] \in \{0,1\} \label{eq10} \\
    & \forall_{i \in [0..f-2]} ~ change[{i}] = 1 \iff state[{i}] = BYE \wedge state[{i+1}] \neq BYE \label{eq11} \\
    & totalChange = \sum_{i=0}^{f-2} ~ change[{i}] \label{eq12}
\end{flalign}

@@

\noindent
We are now in a position to model criteria 1 (each skipper sails against every other skipper) and optimisation criteria 10 (minimise boat changes).  In (\ref{eq13}), (\ref{eq14})  and (\ref{eq15}) we present a
match-perspective of the schedule, using a two dimensional array of variables $match$, where $match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a match. Only the half above the diagonal is represented and the lower half is made up of exactly the same variables, i.e. $match[{i,j}]$ is \emph{exactly} the same constrained variable as $match[{j,i}]$.  Constraint (\ref{eq15}) states that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$ (i.e. $match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time slot is skipper $s[{i}]$.  Constraints (\ref{eq16}), (\ref{eq17})  and (\ref{eq18}) then convert this from time slots to flights, i.e. $modMatch[{i,j}]$ is the flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match. Finally, constraint (\ref{eq19}) ensures that each skipper's match occurs in different flights. Also, since $modMatch[{i,j}] \equiv modMatch[{j,i}]$, setting rows to be all different also ensures that columns are all different.

%
% the match array
%
\begin{flalign}
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match[{i,j}] \in \{0..t-1\} \label{eq13} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match[{j,i}] \equiv match[{i,j}] \label{eq14} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \forall_{k \in [0..t-1]} ~ match[{i,j}] = k \iff s[{i}].timeSlot[{k}] = j  ~ \wedge ~ s[{j}].timeSlot_{k} = i  \label{eq15} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch[{i,j}] \in \{0..f-1\} \label{eq16} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch[{j,i}] \equiv modMatch[{i,j}] \label{eq17} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch[{i,j}] = \frac{match[{i,j}]}{m} \label{eq18} \\
    & \forall_{i \in [0..n-1]} ~ allDifferent(modMatch[{i}]) \label{eq19}
\end{flalign}

\noindent
We now take a temporal view (\ref{eq20}), such that $time[{\tau}]$ is a pair $(i,j)$, stating that at time $\tau$ skippers $s[{i}]$ and $s[{j}]$ are in a match, i.e. we channel between the match-perspective and the temporal-perspective.
%
% one dimensional time and decision variables
%
\begin{flalign}
    & \forall_{\tau \in [0..t-1]} ~ time[{\tau}] \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ time[{\tau}] = (i,j) \iff match[{i,j}] = \tau \label{eq21}
\end{flalign}

@@

%
% optimisation criteria 10
%
\begin{flalign}
    & totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].totalChange  \label{eq22} \\
& minimise(totalBoatChanges) \label{eq23}
\end{flalign}

Figure \ref{schedChanges} gives a pictorial view of the model, using the 7 skipper and 6 boat problem. On the right we have the 7 skippers with their states and time slots. Again, top right, we give the schedule actually produced.  Middle left we have the $match$ array and at the bottom the $time$ array. Above the $match$ array we have the $modMatch$ array. The yellow arrows show the channeling between parts of the model.

\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{schedule.pdf}
%\vspace{-35mm}
\caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats. The schedule is reproduced top right. On the right we have the 7 skippers, on top left the $modMatch$ array, at the bottom $time$ and middle left the $match$ array. The yellow arrows signify channeling between parts of the model.}
\label{schedChanges} 
\end{figure}

The decision variables are $time[{0}]$ to $time[{t-1}]$, i.e. for each time slot we decide what match takes place. A symmetry break is made at the top of search by forcing the first round to contain the matches (0,1), (2,3), ... i.e. $\forall_{i \in [0..m-1]} ~ match[{2.i,2i+1}] = i$. The schedule presented has 6 boat changes: there are no boat changes in flight 0 (first flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and last flight skipper 1.

\subsection{Stage 2 and 3: minimising imbalance and renaming skippers}
Having produced a schedule that minimises boat changes, we then minimise criteria 6, imbalance. Assuming the first stage produced a schedule with $\beta$ boat changes we post this as a hard constraint in stage 2, i.e. $totalBoatChanges \leq \beta$. For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e. in the $i^{th}$ match of the  $j^{th}$ flight (\ref{posB}). Imbalance is then computed via (\ref{imbA}) for each position, as the absolute amount of over or under expected presence in a given postion. Finally, (\ref{imbB}) we compute the maximum imbalance over all positions for this skipper.

\begin{flalign}
    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position[{i,j}] \in \{0,1\} \label{posA} \\
    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position[{i,j}] = 1 \iff \sigma.timeSlot[{m.j+i}] \geq 0 \label{posB} \\
    & \forall_{i \in [0..m-1]} ~ imbalance[{i}] = |\frac{n-1}{m} - \sum_{j=0}^{f-1} position[{i,j}]| \label{imbA} \\
& \sigma.maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
\end{flalign}

@@

\begin{flalign}
    & \forall_{i \in [0..n-1]} ~ imbalance[{i}] = \sigma[{i}].maxImbalance \label{balAllA} \\
& maxImbalance = maximum(imbalance) \label{balAllB} \\
& minimise(maxImbalance) \label{balAllC}
\end{flalign}

>>>>

\newcommand{\match}{\mathit{match}}
\newcommand{\timeSlot}{\mathit{timeSlot}}
\newcommand{\state}{\mathit{state}}
\newcommand{\change}{\mathit{change}}
\newcommand{\totalChange}{\mathit{totalChange}}
\newcommand{\totalBoatChanges}{\mathit{totalBoatChanges}}
\newcommand{\modMatch}{\mathit{modMatch}}
\newcommand{\position}{\mathit{position}}
\newcommand{\imbalance}{\mathit{imbalance}}
\newcommand{\maxImbalance}{\mathit{maxImbalance}}

\newcommand{\globalCardinality}{\mathrm{globalCardinality}}
\newcommand{\allDifferent}{\mathrm{allDifferent}}

@@

The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
of his schedule in the array of constrained integer variables $\timeSlot[0]$
to $\timeSlot[{t-1}]$ (equation \ref{eq3} below), and a state view in the array of
constraint integer variables $\state[0]$ to $\state[{f-1}]$ (equation \ref{eq4}
below), i.e. $\state[i]$ is the state of this skipper in flight $i$ and
corresponds to timeslots $\timeSlot[{i*m}]$ to $\timeSlot[{m(i+1)-1}]$.

\begin{flalign}
& f = \lceil n(n-1)/m  \rceil \label{eq1} \\
& t = n(n-1)/2 \label{eq2} \\
& \forall_{\tau \in [0..t-1]} ~ \timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
& \forall_{i \in [0..f-1]} ~ \state[{i}] \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = FIRST \iff \timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ \timeSlot[{j}] \geq 0  \label{eq6} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = LAST \iff \timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -1  \label{eq8} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
& \globalCardinality(\timeSlot,\{0,..,n-1\} \setminus \{\sigma\},\{1..1\},\{1 .. 1\})
\end{flalign}

In (\ref{eq3}) the array $\timeSlot$ is defined and in (\ref{eq4}) $\state$ is defined. If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a match with skipper $k$ at time $i$. Variable $\state[{i}]$ gives the state of this skipper in flight $i$. The skipper can be in a match in the first time slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{... actually, not first and not last.} (\ref{eq6}) or in the last time slot of the flight (\ref{eq7}). If all time slots in a flight are equal to -1 then the skipper is in a bye (\ref{eq8}) and if all time slots in a flight are equal to -2 then the skipper has finished all his matches (\ref{eq9}).

A global cardinality constraint \cite{globCard} is then imposed on the array $\timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all other skippers (i.e. $\{0 .. n-1 \} \setminus \{\sigma\}$) once (i.e. $\{1 .. 1\}$) and once only (i.e. $\{1 .. 1\}$). The $\state$ variables are then used to impose match race criteria 4 (if last in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then flight $i$ is not first). In addition, we have the rule that if a skipper has finished his matches in flight $i$ (i.e. END) then he has finished his matches in flight $i+1$ (and so on). These criteria are imposed on the $\state$ variables via a deterministic finite automata (dfa) constraint \cite{Pesant04}.

The constraints above are shown pictorially in Figure \ref{skipper5}, and corresponds to skipper 5 in the Table \ref{tab1} schedule. The $\state$ array is presented as coloured boxes, and below that the $\timeSlot$ array. The arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The $\state$ array is coloured with green representing LAST, yellow for MID, blue for FIRST, red for LAST and (not shown) pink for BYE. The schedule of Table \ref{tab1} is reproduced with the matches for skipper 5 emboldened. To the right of the schedule is schema for the dfa. Coloured arc represent a transition from one state to another. The dfa is encoded as a set of transition objects $\langle q_{i},\iota,q_{j} \rangle$ where a transition is made from state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we specify the accepting states, being all states except the start state (white) and bye state (pink).

A boat change occurs when a skipper has been in a BYE state in flight $i$ and then is in a match in the next flight $i+1$. This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $\totalChange$ (\ref{eq12}).

\begin{flalign}
    & \forall_{i \in [0..f-2]} ~ \change[{i}] \in \{0,1\} \label{eq10} \\
    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = BYE \wedge \state[{i+1}] \neq BYE \label{eq11} \\
    & \totalChange = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
\end{flalign}

@@

\noindent
We are now in a position to model criteria 1 (each skipper sails against every other skipper) and optimisation criteria 10 (minimise boat changes).  In (\ref{eq13}), (\ref{eq14})  and (\ref{eq15}) we present a
match-perspective of the schedule, using a two dimensional array of variables $\match$, where $\match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a match. Only the half above the diagonal is represented and the lower half is made up of exactly the same variables, i.e. $\match[{i,j}]$ is \emph{exactly} the same constrained variable as $\match[{j,i}]$.  Constraint (\ref{eq15}) states that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$ (i.e. $\match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time slot is skipper $s[{i}]$.  Constraints (\ref{eq16}), (\ref{eq17})  and (\ref{eq18}) then convert this from time slots to flights, i.e. $\modMatch[{i,j}]$ is the flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match. Finally, constraint (\ref{eq19}) ensures that each skipper's match occurs in different flights. Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows to be all different also ensures that columns are all different.

%
% the match array
%
\begin{flalign}
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~\match[{i,j}] \in \{0..t-1\} \label{eq13} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~\match[{j,i}] \equiv \match[{i,j}] \label{eq14} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \forall_{k \in [0..t-1]} ~ \match[{i,j}] = k \iff s[{i}].\timeSlot[{k}] = j  ~ \wedge ~ s[{j}].\timeSlot[{k}] = i  \label{eq15} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \modMatch[{i,j}] \in \{0..f-1\} \label{eq16} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \modMatch[{j,i}] \equiv \modMatch[{i,j}] \label{eq17} \\
    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \modMatch[{i,j}] = \frac{\match[{i,j}]}{m} \label{eq18} \\
    & \forall_{i \in [0..n-1]} ~ \allDifferent(\modMatch[{i}]) \label{eq19}
\end{flalign}

\noindent
We now take a temporal view (\ref{eq20}), such that $time[{\tau}]$ is a pair $(i,j)$, stating that at time $\tau$ skippers $s[{i}]$ and $s[{j}]$ are in a match, i.e. we channel between the match-perspective and the temporal-perspective.
%
% one dimensional time and decision variables
%
\begin{flalign}
    & \forall_{\tau \in [0..t-1]} ~ time[{\tau}] \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ time[{\tau}] = (i,j) \iff \match[{i,j}] = \tau \label{eq21}
\end{flalign}

@@

%
% optimisation criteria 10
%
\begin{flalign}
    & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChange  \label{eq22} \\
& minimise(\totalBoatChanges) \label{eq23}
\end{flalign}

Figure \ref{schedChanges} gives a pictorial view of the model, using the 7 skipper and 6 boat problem. On the right we have the 7 skippers with their states and time slots. Again, top right, we give the schedule actually produced.  Middle left we have the $\match$ array and at the bottom the $time$ array. Above the $match$ array we have the $\modMatch$ array. The yellow arrows show the channeling between parts of the model.

\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{schedule.pdf}
%\vspace{-35mm}
\caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats. The schedule is reproduced top right. On the right we have the 7 skippers, on top left the $\modMatch$ array, at the bottom $time$ and middle left the $\match$ array. The yellow arrows signify channeling between parts of the model.}
\label{schedChanges} 
\end{figure}

The decision variables are $time[{0}]$ to $time[{t-1}]$, i.e. for each time slot we decide what match takes place. A symmetry break is made at the top of search by forcing the first round to contain the matches (0,1), (2,3), ... i.e. $\forall_{i \in [0..m-1]} ~ \match[{2.i,2i+1}] = i$. The schedule presented has 6 boat changes: there are no boat changes in flight 0 (first flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and last flight skipper 1.

\subsection{Stage 2 and 3: minimising imbalance and renaming skippers}
Having produced a schedule that minimises boat changes, we then minimise criteria 6, imbalance. Assuming the first stage produced a schedule with $\beta$ boat changes we post this as a hard constraint in stage 2, i.e. $\totalBoatChanges \leq \beta$. For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e. in the $i^{th}$ match of the  $j^{th}$ flight (\ref{posB}). Imbalance is then computed via (\ref{imbA}) for each position, as the absolute amount of over or under expected presence in a given postion. Finally, (\ref{imbB}) we compute the maximum imbalance over all positions for this skipper.

\begin{flalign}
    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] \in \{0,1\} \label{posA} \\
    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] = 1 \iff \sigma.\timeSlot[{m.j+i}] \geq 0 \label{posB} \\
    & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = |\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]| \label{imbA} \\
& \sigma.\maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
\end{flalign}

@@

\begin{flalign}
    & \forall_{i \in [0..n-1]} ~ \imbalance[{i}] = \sigma[{i}].\maxImbalance \label{balAllA} \\
& \maxImbalance = maximum(\imbalance) \label{balAllB} \\
& minimise(\maxImbalance) \label{balAllC}
\end{flalign}
